{{< include _setup.qmd >}}

# CS Kernel

### Kernel Specification {.unnumbered}

Will update this later.

### Simulation {.unnumbered}

Simulate CS data.

<div class="vcenter-cols">
::: {.columns}
::: {.column width="40%"}

```{r}
set.seed(1)

time <- 5
params_cs_true <- list(
  mu = 5,
  K = 0.5,
  beta = 2,
  beta_edges = 0.5,
  node_lambda = 4,
  # CS_edges = -2.5,
  # CS_triangles = 0.001,
  CS_star.2 = -1,
  CS_star.3 = -3
)

sim <- sim_hawkesNet(
  params = params_cs_true,
  T_end = time,
  mark_type = "cs",
  # formula_rhs = "edges + triangles() 
  # + star(c(2,3))",
  formula_rhs = "star(c(2,3))"
)
```
:::
::: {.column width="60%"}

```{r fig.width=8, fig.height=8, out.width="100%", echo = FALSE}
op <- par(no.readonly = TRUE)
on.exit(par(op), add = TRUE)

par(mar = c(1,1,1,1), xaxs = "i", yaxs = "i")
plot(sim$net)
```
:::
:::
</div>

### Model fitting {.unnumbered}


Fit CS data. 

:::callout-tip
Make sure to specify the transformation setting for the CS parameters. 

Ideally will default to correct value, but want to discuss how we are implementing
the arguments, because lowk I like the old way of passing `CS_params` better.
:::

```{r}
params_cs_init <- list(
  mu = 3,
  K = 1,
  beta = 1,
  beta_edges = 1,
  node_lambda = 5,
  # CS_edges = -2.5,
  # CS_triangles = 0.001,
  CS_star.2 = 0,
  CS_star.3 = 0
)

fit <- fit_hawkesNet(
      ev = sim$ev,
      params_init = params_cs_init,
      mark_type = "cs",
      transform = list(CS_star.2 = "none", CS_star.3 = "none"),
      formula_rhs = "star(c(2,3))"
    )
```

Parameter values on the fitted scale:

```{r}
unlist(fit$par)
```

Parameter values on the transformed scale:

```{r}
fit$fit$par
```



