{{< include _setup.qmd >}}

# CS-Bipartite Kernel

### Kernel Specification {.unnumbered}

Nodes have two possible classifications / types / modes - events / perps.

Each mark consists of exactly 1 new event node arriving, which connects to old 
perp nodes according to the same degree-based weighting above. Additionally, 
each mark consists of n ~ Pois(lambda_new) perp nodes, which are attached to the 
new event node.

:::callout-note
Literally exactly the same as using the CS kernel, but all you need to do is
specify `mark_type = "cs_bip"`.
:::

### Simulation {.unnumbered}

Simulate CS data.

<div class="vcenter-cols">
::: {.columns}
::: {.column width="40%"}

```{r}
set.seed(1)

time <- 10
params_cs_bip_true <- list(
  mu = 2,
  K = 0.5,
  beta = 2,
  beta_edges = 0.5,
  lambda_new = 2,
  # CS_edges = -2.5,
  # CS_triangles = 0.001,
  CS_star.2 = -1,
  CS_star.3 = -3
)

sim <- sim_hawkesNet(
  params = params_cs_bip_true,
  T_end = time,
  mark_type = "cs_bip",
  # formula_rhs = "edges + triangles() + star(c(2,3))",
  formula_rhs = "star(c(2,3))"
)
```

:::
::: {.column width="60%"}

```{r fig.width=8, fig.height=8, out.width="100%", echo = FALSE}
col_map <- c(
  event = "#377EB8",
  perp  = "#E41A1C"
)

roles <- network::get.vertex.attribute(sim$net, "role")
cols <- col_map[roles]

op <- par(no.readonly = TRUE)
on.exit(par(op), add = TRUE)

# Add a little bottom space for legend
par(mar = c(2.5,1,1,1), xaxs = "i", yaxs = "i")

plot(sim$net, vertex.col = cols)

legend(
  "bottomleft",
  legend = c("Event", "Perp"),
  pch = 21,
  pt.bg = col_map[c("event", "perp")],  # fill colour
  col = "black",                        # border colour
  horiz = TRUE,
  inset = 0.01,
  xpd = TRUE,
  cex = 2,
  pt.cex = 2.5
)
```

:::
:::
</div>

### Model fitting {.unnumbered}

Fit CS data. 

:::callout-tip
Make sure to specify the transformation setting for the CS parameters. 

Ideally will default to correct value, but want to discuss how we are implementing
the arguments, because lowk I like the old way of passing `CS_params` better.
:::

```{r}
params_cs_bip_init <- list(
  mu = 3,
  K = 1,
  beta = 1,
  beta_edges = 1,
  lambda_new = 5,
  # CS_edges = -2.5,
  # CS_triangles = 0.001,
  CS_star.2 = 0,
  CS_star.3 = 0
)

fit <- fit_hawkesNet(
      ev = sim$ev,
      params_init = params_cs_bip_init,
      mark_type = "cs_bip",
      transform = list(CS_star.2 = "none", CS_star.3 = "none"),
      formula_rhs = "star(c(2,3))"
    )
```

Parameter values on the fitted scale:

```{r}
unlist(fit$par)
```

:::callout-note
Estimates don't look great @_@
:::

Parameter values on the transformed scale:

```{r}
fit$fit$par
```

::: {.callout-note collapse="true"}
## See the simulation study results for the CS-BIP kernel here.
:::



