{{< include _setup.qmd >}}

# CS-Bipartite Examples

:::callout-note
Literally exactly the same as using the CS kernel, but all you need to do is
specify `mark_type = "cs_bip"`.
:::

Simulate CS data.

```{r}
set.seed(1)

time <- 10
params_cs_bip_true <- list(
  mu = 2,
  K = 0.5,
  beta = 2,
  beta_edges = 0.5,
  lambda_new = 2,
  # CS_edges = -2.5,
  # CS_triangles = 0.001,
  CS_star.2 = -1,
  CS_star.3 = -3
)

sim <- sim_hawkesNet(
  params = params_cs_bip_true,
  T_end = time,
  mark_type = "cs_bip",
  # formula_rhs = "edges + triangles() + star(c(2,3))",
  formula_rhs = "star(c(2,3))"
)
```

:::callout-note
Need to discuss the `triangles()` parameter. I think the current calculation of
change statistics for triangles is incorrect.
:::

```{r}
# Bipartite colouring
col_map <- c(
  event = "#377EB8",
  perp  = "#E41A1C"
)
roles <- network::get.vertex.attribute(sim$net, "role")
cols <- col_map[roles]

plot(sim$net, vertex.col = cols)
```

```{r}
print(paste("Number of simulated nodes:", nrow(sim$ev$nodes)))
paste("Number of simulated edges:", nrow(sim$ev$edges))
paste("Number of simulated events:", sim$events$n)
```

Fit CS data. 

:::callout-tip
Make sure to specify the transformation setting for the CS parameters. 

Ideally will default to correct value, but want to discuss how we are implementing
the arguments, because lowk I like the old way of passing `CS_params` better.
:::

```{r}
params_cs_bip_init <- list(
  mu = 3,
  K = 1,
  beta = 1,
  beta_edges = 1,
  lambda_new = 5,
  # CS_edges = -2.5,
  # CS_triangles = 0.001,
  CS_star.2 = 0,
  CS_star.3 = 0
)

fit <- fit_hawkesNet(
      ev = sim$ev,
      params_init = params_cs_bip_init,
      mark_type = "cs_bip",
      transform = list(CS_star.2 = "none", CS_star.3 = "none"),
      formula_rhs = "star(c(2,3))"
    )
```

Parameter values on the fitted scale:

```{r}
unlist(fit$par)
```

:::callout-note
Estimates don't look great @_@
:::

Parameter values on the transformed scale:

```{r}
fit$fit$par
```



